### 2020-04-15 intro.tex
more fix section refs

We begin by describing related work in Sec.~\ref{section:related}. Our
data collection is desctibed in Sec.~\ref{section:dataprep} and the data
cleaning, checking, and lifetime summarization process in
Sec.~\ref{section:dataclean}. A timme between failures analysis is given
in Sec.~\ref{section:tbf}. Survival analysis based on Kaplan-Meier
modeling and Cox regression modeling of relative hazard rates are in
Sec.~\ref{section:survival}. Finally, we discuss our main conclusions and
recommendations in Sec.~\ref{section:discussion}.

>>>>

We begin by describing related work in Sec.~\ref{section:related}. Our
data collection is desctibed in Sec.~\ref{section:dataprep} and the
data cleaning, checking, and lifetime summarization process in
Sec.~\ref{section:dataclean}. A time between failures (TBF) analysis
is given in Sec.~\ref{section:tbf}. Survival analysis based on
Kaplan-Meier modeling (KM) and Cox regression modeling (CR) of
relative hazard rates in various locations are in
Sec.~\ref{section:survival}. Finally, we discuss our main conclusions
and recommendations in Sec.~\ref{section:discussion}.
